#Megan Liska
#HW 4

##Question1
###a).
Create the vector (1,2,3...19,20)
```{r}
c(1:20)
```
###b).
Create the vector (20,19,18...2,1)
```{r}
c(20:1)
```
###c).
Create the vecotr (1,2,...19,20,19,,,1)
```{r}
c(1:20,19:1)
```
###d).
Create the vector (4,6,3) and assign it the name tmp
```{r}
tmp <- c(4,6,3)
tmp
```
###e).
repeats vector tmp 10 times.
 rep repeats the first argument 
```{r}
rep(tmp,10) 
```
###f). 
```{r}
rep(tmp,l=31)
```
Makes the vector where 4 occurs 11 times and 6 and 3 occur 10 times
###g).
makes tmp where there are 10 4's in a row, 20 6's and then 30 3's
```{r}
rep(tmp,times = c(10,20,30))
```

##Question 2
Create a vector of the values of e^xcos(x) at x=3,3.1,3.2...5.9,6.
 seq builds a vector of values from 3 to 6 incriminted by .1 
```{r}
x <- seq(3,6,by=0.1) 
exp(x)*cos(x) 
```

##Question 3
###a).
```{r}
(0.1^seq(3,36,by=3))*(0.2^seq(1,34,by=3))
```
###b).
```{r}
(2^seq(1,25,by=1))/(1:25) 
```
##Question 4
###a).
create i which goes from 1 to 100 incrimented by 1. Sum creates an finite sum of the values of i
```{r}
i <- seq(1,100,by=1) 
sum(i^3+4*i^2) 
```
###b).
same process as part a
```{r}
i <- seq(1,25) 
sum(2^i/i + 3^i/i^2)
```

##Question 5
###a).
Use function paste to create vectors of length 30.
paste converts its arguments into charcter strings and then seperates them by sep (second argument)
```{r}
paste('label',1:30) 
```
###b).
make sure no space between fn and number by using sep = ""
```{r}
paste('fn',1:30,sep = "")
```
##Question 6
Execute the following lines which creates two vectors of random integers with length 250
```{r}
set.seed(50) 
xVec <- sample(0:999,250,replace=T) 
yVec <- sample(0:999,250,replace=T)
```

###a).
create vector (y2-x1,...,yn-xn-1)
```{r}
yVec[c(2:250)]-xVec[c(1:249)]
```
###b).
Create vector sin(y1)/cos(x2),...sin(yn-1)/cos(n)
```{r}
sin(yVec[c(1:249)])/cos(xVec[c(2:250)])
```
###c).
create vector x1-2x2-x3-...-xn
```{r}
xVec[c(1:248)]+2*xVec[c(2:249)]-xVec[c(3:250)]
```
###d).
sum calculates the sum from i=1 to n-1
```{r}
sum(exp(-xVec[c(2:250)])/(xVec[c(1:249)]+10)) 
```
##Question 7 
We use the same random vectors from 6
```{r}
set.seed(50)
xVec <- sample(0:999,250,replace=T)
yVec <- sample(0:999,250,replace=T)
```
###a).
Pick the values in yVec which are >600
```{r}
y600 <- yVec[yVec > 600]
y600
```
###b).
Finds the index positions in yVec of the values which are >600
```{r}
which(yVec > 600)
```
###c).
Finds the values in xVec which correspond to values in yVec which are > 600?
```{r}
x600 <- xVec[yVec>600]
x600
```
###d).

```{r}
sqrt(abs(xVec - mean(xVec)))
```
###e).
Finds how many values in yVec are within 200 of the max value
```{r}
sum(yVec > max(yVec) - 200)
```
###f).
Finds how many values in xVec are divisible by 2.
Note %% is the mod operator
```{r}
sum(xVec%%2==0)
```
###g).
Sorts the numbers in xVec in the order of increasing values in yVec
```{r}
xVec[order(yVec)]
```
###h).
Picks out the elements in yVec at the index positions 1,4,7,10...

```{r}
yVec[c(T,F,F)]
```
c(T,F,F) takes the first element out of every three elements.
##Question 8
cumprod takes the cumulative product of an array of elements
```{r}
1+sum(cumprod(seq(2,38,by=2)/seq(3,39,by=2))) 
```
