#Megan Liska
#HW 4

##Question1
###a).
```{r}
c(1:20)
```
###b).
```{r}
c(20:1)
```
###c).
```{r}
c(1:20,19:1)
```
###d).
```{r}
tmp <- c(4,6,3) 
```
###e).
rep repeats the first argument 
```{r}
rep(tmp,10) 
```
###f). 
```{r}
rep(tmp,l=31)
```
###g).
```{r}
rep(tmp,times = c(10,20,30))
```

##Question 2
seq builds a vector of values from 3 to 6 incriminted by .1 
```{r}
x <- seq(3,6,by=0.1) 
exp(x)*cos(x) 
```

##Question 3
###a).
```{r}
(0.1^seq(3,36,by=3))*(0.2^seq(1,34,by=3))
```
###b).
```{r}
(2^seq(1,25,by=1))/(1:25) 
```
##Question 4
###a).
create i which goes from 1 to 100 incrimented by 1. Sum creates an finite sum of the values of i
```{r}
i = seq(1,100,by=1) 
sum(i^3+4*i^2) 
```
###b).
same process as part a
```{r}
i = seq(1,25,by=1) 
sum(2^i/i + 3^i/i^2)
```

##Question 5
###a).
paste converts its arguments into charcter strings and then seperates them by sep (second argument)
```{r}
paste('label',1:30) 
```
###b).
make sure no space between fn and number by using sep = ""
```{r}
paste('fn',1:30,sep = "")
```
##Question 6
Execute the following lines which creates two vectors of random integers with length 250
```{r}
set.seed(50) 
xVec <- sample(0:999,250,replace=T) 
yVec <- sample(0:999,250,replace=T)
```

###a).
```{r}
yVec[c(2:250)]-xVec[c(1:249)] #subtracts x from y
```
###b).
```{r}
sin(yVec[c(1:249)])/cos(xVec[c(2:250)])
```
###c).
```{r}
xVec[c(1:248)]+2*xVec[c(2:249)]-xVec[c(3:250)]
```
###d).
sum calculates the sum
```{r}
sum(exp(-xVec[c(2:250)])/(xVec[c(1:249)]+10)) 
```
##Question 7 
We use the same random vectors from 6
```{r}
set.seed(50)
xVec <- sample(0:999,250,replace=T)
yVec <- sample(0:999,250,replace=T)
```
###a).
```{r}
y600 <- yVec[yVec>600]
y600
```
###b).
```{r}
which(yVec>600)
```
###c).
```{r}
x600<-xVec[yVec>600]
```
###d).
```{r}
sqrt(abs(xVec-mean(xVec)))
```
###e).
```{r}
sum(yVec>max(yVec)-200)
```
###f).
```{r}
sum(xVec%%2==0)
```
###g).
```{r}
xVec[order(yVec)]
```
###h).
```{r}
yVec[c(T,F,F)]
```

##Question 8
cumprod takes the cumulative product of an array of elements
```{r}
1+sum(cumprod(seq(2,38,by=2)/seq(3,39,by=2))) 
```
