#Megan Liska
#HW 4

##Question1
###a).
```{r}
c(1:20)
```
###b).
```{r}
c(20:1)
```
###c).
```{r}
c(1:20,19:1)
```
###d).
```{r}
tmp <- c(4,6,3) 
```
###e).
rep repeats the first argument 
```{r}
rep(tmp,10) 
```
###f). 
```{r}
rep(tmp,l=31)
```
###g).
rep(tmp,times = c(10,20,30))

##Question 2
###seq builds a vector of values from 3 to 6 incriminted by .1 
x <- seq(3,6,by=0.1) 
exp(x)*cos(x) 

##Question 3
###a).
(0.1^seq(3,36,by=3))*(0.2^seq(1,34,by=3))
###b).
(2^seq(1,25,by=1))/(1:25) 

##Question 4
###a).create i which goes from 1 to 100 incrimented by 1. Sum creates an finite sum of the values of i
i = seq(1,100,by=1) 
sum(i^3+4*i^2) 
###b).same process as part a 
i = seq(1,25,by=1) 
sum(2^i/i + 3^i/i^2)

##Question 5
###a).paste converts its arguments into charcter strings and then seperates them by sep (second argument)
paste('label',1:30) 

###b).make sure no space between fn and number by using sep = ""
paste('fn',1:30,sep = "")

##Question 6
###Execute the following lines which creates two vectors of random integers with length 250
set.seed(50) 
xVec <- sample(0:999,250,replace=T) 
yVec <- sample(0:999,250,replace=T)


###a).
yVec[c(2:250)]-xVec[c(1:249)] #subtracts x from y
###b).
sin(yVec[c(1:249)])/cos(xVec[c(2:250)])
###c).
xVec[c(1:248)]+2*xVec[c(2:249)]-xVec[c(3:250)]
###d).sum calculates the sum
sum(exp(-xVec[c(2:250)])/(xVec[c(1:249)]+10)) 

##Question 7 
###We use the same random vectors from 6
set.seed(50)
xVec <- sample(0:999,250,replace=T)
yVec <- sample(0:999,250,replace=T)
###a).
y600 <- yVec[yVec>600]
y600
###b).
which(yVec>600)
###c).
x600<-xVec[yVec>600]
###d).
sqrt(abs(xVec-mean(xVec)))
###e).
sum(yVec>max(yVec)-200)
###f).
sum(xVec%%2==0)
###g).
xVec[order(yVec)]
###h).
yVec[c(T,F,F)]

##Question 8
###cumprod takes the cumulative product of an array of elements
1+sum(cumprod(seq(2,38,by=2)/seq(3,39,by=2))) 
